Methods for Large Scale Learning to Rank

### 2014-11-13 report/Chapters/Results.tex
verder aan presentatie
presentatie Avanade af + eerste feedbackpuntjes Dolf

\subsection{Ranking accuracy}
To validate our ListNet cluster implementation we run experiments on the LETOR 3.0 OHSUMED, the LETOR 4.0 datasets MQ2007 and MQ2008 and compare their performance with the RankLib implementation of ListNet and with the official evaluation results in terms of \ac{NDCG}@10. Hadoop job scheduling overhead is large when processing relatively small datasets (as we will explain in more detail in section \ref{ssec:speedup}), therefore \ac{NDCG}@10 experiments are limited to five training iterations and are run only on one of the five folds. Because of the stochastic nature of the ListNet ranking procedure, which is a result of random weight initialisation prior to the first training iteration, the \ac{NDCG}@10 performance is not guaranteed to be identical between multiple runs on the same input data. To account for this non-determinism of ListNet, we repeat each experiment five times and report the average as well as the standard deviation of the resulting rankings on the testing fold in terms of \ac{NDCG}@10.\\

@@

\begin{table}
\centering
\begin{tabular}{p{3.4cm}p{2.6cm}p{2.6cm}p{2.6cm}}\toprule
 &  OHSUMED (LETOR 3.0 version) & MQ2008 & MQ2007 \\
\midrule
RankLib                             & 0.1916 $\pm$ 0.0634 & 0.3889 $\pm$ 0.0600 & 0.2918 $\pm$ 0.0546 \\
Cluster \newline (no preprocessing)	& 0.2212 $\pm$ 0.0564 & 0.3496 $\pm$ 0.0788 & 0.2846 $\pm$ 0.0891\\
Cluster \newline (preprocessing)    & 0.3395 $\pm$ 0.0952 & 0.4280 $\pm$ 0.0998 & 0.4554 $\pm$ 0.0085\\
Official evaluation                 & 0.3793 & 0.4689 & 0.4767 \\
\bottomrule
\end{tabular}
\caption{\acs{NDCG}@10 performance on the test set of the first fold}
\label{tbl:accuracy_comparison}
\end{table}

>>>>

\subsection{Ranking accuracy}
To validate our ListNet cluster implementation we run experiments on the LETOR 3.0 OHSUMED, the LETOR 4.0 datasets MQ2007 and MQ2008 and compare their performance with the RankLib implementation of ListNet and with the official evaluation results in terms of \ac{NDCG}@10. Hadoop job scheduling overhead is relatively large when processing relatively small datasets (as we will explain in more detail in section \ref{ssec:speedup}), therefore \ac{NDCG}@10 experiments are limited to five training iterations and are run only on one of the five folds. Because of the stochastic nature of the ListNet ranking procedure, which is a result of random weight initialisation prior to the first training iteration, the \ac{NDCG}@10 performance is not guaranteed to be identical between multiple runs on the same input data. To account for this non-determinism in ListNet, we repeat each experiment five times and report the average as well as the standard deviation of the resulting rankings on the testing fold in terms of \ac{NDCG}@10.\\

@@

\begin{table}
\centering
\begin{tabular}{p{3.4cm}p{3.0cm}p{2.6cm}p{2.6cm}}\toprule
 &  OHSUMED  (LETOR 3.0) & MQ2008 & MQ2007 \\
\midrule
RankLib                             & 0.1916 $\pm$ 0.0634 & 0.3889 $\pm$ 0.0600 & 0.2918 $\pm$ 0.0546 \\
Cluster \newline (no preprocessing)	& 0.2212 $\pm$ 0.0564 & 0.3496 $\pm$ 0.0788 & 0.2846 $\pm$ 0.0891\\
Cluster \newline (preprocessing)    & 0.3395 $\pm$ 0.0952 & 0.4280 $\pm$ 0.0998 & 0.4554 $\pm$ 0.0085\\
Official evaluation                 & 0.3793 & 0.4689 & 0.4767 \\
\bottomrule
\end{tabular}
\caption{\acs{NDCG}@10 performance on the test set of the first fold}
\label{tbl:accuracy_comparison}
\end{table}
